\input{fixos/indiceAutomatico}

\hrule	% Linha horizontal
\begin{center} % Minipage Centralizado
\begin{minipage}[c]{12.5cm} % Largura
Autor: \imprimirautor

Tema: \imprimirtitulo 
\imprimirlocal,\\ 
\imprimirorientador\\
\hspace{0.5cm}
\parbox[t]{\textwidth}{\imprimirinstituicao
\imprimirdata.}\\
\hspace{0.5cm}
\end{minipage}
\end{center}
\hrule

\vspace{1cm}

\SingleSpacing
\noindent
{\textbf{LEARNING ARTIFICIAL INTELLIGENCE THROUGH ARTIFICIAL MEMORIES}}
\indent
\small

In order to direct the research of this work, a systematic mapping was carried out with the objective of investigating the possibility of creating a system that uses artificial intelligence to simulate human attitudes. Memories and attitudes contribute to the construction of consciousness and human character. Whether they are good events or not. In the case of memories, the conscious directs to the attitudes, demanding less processing of the brain. Artificial intelligence uses this same principle for its development, that is, the use of artificial memories can simulate human attitudes.Inclusion and exclusion criteria were selected to select the publications that best fit the problem.The publications were selected and categorized in each area of action, ie, artificial intelligence and decision making. As future works, the possibility of creating systems that use artificial memories and learning with these memories to simulate human attitudes is observed.

\noindent
 
\textbf{Keywords}: Intelligence,Artificial,Memories,Humans,Technology,Modern,World,
\\Consciousness,Brain.

\SingleSpacing
\noindent
{\textbf{APRENDIZADO DE INTELIGÊNCIA ARTIFICIAL ATRAVÉS DE MEMÓRIAS ARTIFICIAIS}}
\indent
\small

Com o intuito de direcionar a pesquisa deste trabalho, foi realizado um mapeamento sistemático com o objetivo de investigar a possibilidade de criação de um sistema que utilize inteligência artificial para simular atitudes humanas. Memórias e atitudes contribuem para a construção do consciente e do caráter humano. Sejam acontecimentos bons ou não. No caso das memórias, o consciente direciona às atitudes, demandando menos processamento do cérebro. A inteligência artificial usa desse mesmo princípio para o seu desenvolvimento, ou seja, a utilização de memórias artificiais pode simular atitudes humanas. Foram feitos critérios de inclusão e exclusão para selecionar as publicações que melhor se enquadram para a solução do problema. As publicações foram selecionadas e foram categorizadas em cada área de atuação, ou seja, inteligência artificial e tomada de decisões. Como trabalhos futuros observa-se a possibilidade de criação de sistemas que utilizem memórias artificiais e aprendizado com essas memórias para a simulação de atitudes humanas.

\noindent
 
\textbf{Palavras-Chave}: Inteligência,Artificial,Memórias,Humanas,Tecnologia,Moderno,Mundo,
\\Consciência,Cérebro.

\vspace{2cm}

\section{Introdução}
\label{introducao}
\input{editaveis/introducao}

\section{Revisão Sistemática}
\label{sec:revisaosistematica}
\input{editaveis/revisaosistematica}

\vspace{1cm}
\section{Planejamento da Pesquisa}
\label{sec:planejamento}
\input{editaveis/planejamento}

\vspace{1cm}
\section{Execução da Revisão Sistemática}
\label{sec:execucao}
\input{editaveis/execucao}

\vspace{1cm}
\section{Resultados da Revisão Sistemática}
\label{sec:resultados}
\input{editaveis/resultados}

\vspace{1cm}
\section{Considerações Finais}
\label{sec:consideracoes}
\input{editaveis/conclusoes}